R Notebook

### 2020-01-14 src/testing_file.Rmd
ascii combine and separate prep files (for running in bash)

>>>>

#file renaming for the merge and split .csv files

Need csv file of depth and depthlayerno (depth_bin.csv in data/env)

Str sub to split filename…
	- Year month variable
	- Depth

clogasc_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^cloglog_.*.asc", full.names = TRUE)

Then use a loop

for I in length(csv)
Csv_dep == str_sub

For j in length(list)
	Dirdep ==
	If csv == dirdep
	Xx <- list[j]
	Yy <- Str_sub Year month variable
	Layerno <-

	File.rename(xx, paste0(YY, "_", layerno, ".asc")

	    filedep <- str_sub(filen, start = 1, end = 11)

depthlst <- read.csv("../data/env/depth_bin.csv", header = TRUE)
asclst <- list.files("../data/test/ASCII", full.names = FALSE)

for (d in 1:length(depthlst)){
  csvdep <- depthlst$depthlayerno[d]
  for (f in 1:length(asclst)){
    filen <- asclst[3]
    filedep <- str_sub(filen, start = 16, end = -5)
    if csvdep == filedep{

  }
}
```
